
%------------------------------------
%	CV design by Andrew Q. Philips
%	10/26/18
%------------------------------------

\documentclass{article}

% FONT ------------
\usepackage[utf8]{inputenc}
\usepackage{helvet}

% DOCUMENT LAYOUT -----------
\usepackage{geometry} 
\geometry{a4paper, textwidth=6.5in, textheight=9.05in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage{comment}


% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\textbf{Hannah L.\ Paul}}
\renewcommand{\headrulewidth}{0mm}% no header line please!
\AtBeginDocument{\thispagestyle{empty}} % no header on pg. 1


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage{xcolor} % to define color
\definecolor{dkblue}{RGB}{1,0,98} % dk blue link color
\usepackage[bookmarks,
  	colorlinks,
   	breaklinks,
    pdftitle={Hannah L Paul CV},
    pdfauthor={Hannah L Paul}]{hyperref}  
\hypersetup{linkcolor=blue,
	citecolor=blue,
	filecolor=black,
	urlcolor=dkblue} 
	

% DOCUMENT ------------------------------------------
\begin{document}	

{\LARGE Hannah L.\ Paul}			% Name
\vskip 1.4em

\begin{minipage}[t]{.5\textwidth}

Truman School of Government \& Public Affairs\\	% Address
University of Missouri\\ 
615 Locust Street, Columbia, MO 65211


% Email and website
\end{minipage}
\begin{minipage}[t]{.5\textwidth}
\begin{flushright}
\href{mailto:hannah.paul@missouri.edu}{hannah.paul@missouri.edu}\\
\href{https://sites.google.com/colorado.edu/hannahpaul/home}{Hannah's Web Site}\\
%Cell: 214-674-9504\\
\end{flushright}
\end{minipage}


%\subsection*{\textbf{ACADEMIC APPOINTMENTS}}


% Things that should be on the front page of your vitae: the title of your dissertation, list of your committee members, a paragraph abstract describing the dissertation, keywords of what you teach and research, nationally-competitive grants and awards (i.e. Fulbrights, NSF), and publications. 
% list your research interests and your teaching interests on the first page of your vitae.

\subsection*{\textbf{ACADEMIC APPOINTMENTS}}
Assistant Professor of Comparative Public Policy, Truman School of Government \& Public Affairs, University of Missouri. 2022-present.

\subsection*{\textbf{EDUCATION}}
PhD, Department of Political Science, University of Colorado Boulder. 2016-2022.
\vskip .25cm
Concentrations: Comparative Politics, American Politics, Political Methodology \par
Dissertation: Refuge and Representation: The Political Integration of Refugees in Democracies

%\textit{MA}, Political Science, University of Colorado Boulder. 2018. \par
\vskip .25cm

\textit{BA}, Political Science (International Relations), Minor in Asian Studies, Texas Christian University. 2013.  \par
\textit{BA}, Modern Language Studies (French concentration), Texas Christian University. 2013.   \par
\emph{Spring 2011: classes taken at University of Nantes \& Institute for International Education of Students} 
\textit{Magna Cum Laude, Phi Beta Kappa, Departmental Honors}  \par

\subsection*{\textbf{PUBLICATIONS}}
\noindent

Paul, Hannah L., and Jennifer Fitzgerald. (2021) \href{https://www.dropbox.com/s/iap7vdj1mkhpze6/Paul\%20and\%20Fitzgerald\%202021\%20Polity.pdf?dl=0}{``The Dynamics of Issue Salience: Immigration and Public Opinion."} \emph{Polity} 53(3), 370-393. 
\vskip .25cm

Funk, Kendall D., Hannah L. Paul, and Andrew Q. Philips. (2022) \href{https://www.dropbox.com/s/ue64dcghp4e25k7/Funk\%2C\%20Paul\%2C\%20and\%20Philips\%202021\%20PSRM_firstview.pdf?dl=0}{ ``Point break: using machine learning to uncover a critical mass in women's representation."} \emph{Political Science Research and Methods}, 10(2), 372-390. doi:10.1017/psrm.2021.51

\vskip .25cm

Jordan, Soren, Hannah L. Paul, and Andrew Q. Philips. (2022) \href{https://www.dropbox.com/s/6u7fyg58q9ag58u/Jordan\%2C\%20Paul\%20and\%20Philips\%202022\%20LSQ.pdf?dl=0}{``How to Cautiously Uncover the `Black Box' of Machine Learning Models for Legislative Scholars"}, \emph{Legislative Studies Quarterly}

\vskip .25cm

Paul, Hannah L., and Andrew Q. Philips. (2022) \href{https://www.dropbox.com/s/7eiz60coy1ls7te/Paul\%20and\%20Philips\%202022\%20SSQ.pdf?dl=0}{``What Goes up Must Come Down: Modeling Threshold Dynamics."}, \emph{Social Science Quarterly}, 103(5), 1273-1289.

%\subsection*{\textbf{DISSERTATION}}

%\emph{Refuge and Representation: The Integration of Involuntary Migrants into Democracy} \par

%My dissertation research examines the pathways that involuntary migrants take to integrate into the democratic political life in their country of resettlement with a regional focus on the United States and Europe. My research contributes to Political Science by extending research that examines how native-born individuals and voluntary migrants engage in democratic politics to include those with involuntary migration backgrounds. Much of the immigration politics literature treats immigrants as a single group. Using a multi-methods approach, I demonstrate the problematic nature of pooling immigrants from all backgrounds. The distinction between voluntary and involuntary migration reveals important differences in how immigrants engage politics, informing policymakers and advocates about how to improve the political integration of these groups and, by extension, their political representation.   \par
%\vskip .25cm

%\textbf{Dissertation Committee Members}: Jennifer Fitzgerald (chair), Andrew Q. Philips, Carew Boulding, Vanessa Baird, June Gruber

%\vskip .25cm

%\subsection*{\textbf{PUBLICATIONS}}

%\noindent

%Cal, Poli T. 2018. ``The parties are polarized'' \emph{Political Journal} 13(1) 250-280. 
%\vskip .25cm
%Cal, Poli T. 2016. ``Did Nixon cause Watergate?''  \emph{Political Journal}. 13(1) 250-280.


%\subsection*{\textbf{RESEARCH INTERESTS}}
%\textbf{Substantive}: American political behavior, immigration, race and ethnicity, political representation, citizenship, gender and politics \par
%\textbf{Methodological}: Time series, pooled time series, machine learning 


\subsection*{\textbf{WORKING PAPERS Full draft available for any paper listed below upon request}}

``The Localized Effects of Policy Change: A Quasi-Experiment on Gender Quotas and Engagement in Civil Society in India" (with Komal Preet Kaur and Nathan J. Cook) % \textbf{(Status: Under Review)}
\vskip .25cm 
``Refuge and Representation: The Effects of Integration Courses on Refugees' Party Attachments in Germany"  
\vskip .25cm
``Personalizing Politics: An Experimental Examination of the Effect of a Refugee's First-Person Narrative on Political Attitudes"
\vskip .25cm 
``Personalized Politics: An Experimental Analysis of How Perceptions about Political Leaders Shape Refugees' Political Trust" (with Wendy Hansen and Prakash Adhikari)
\vskip .25cm
``Empathy as an Explanation for Support for Immigrants: An Analysis of Immigration Attitudes in Sweden." 
\vskip .25cm
``When Personal and Political Salience Align: A Cross-National Analysis of Identity and Voter Turnout."
\vskip .25cm
%``Diverse Networks and Political Tolerance: An Analysis of the Factors that Shape Political Tolerance in the United States." (with Kimi Killen) 

%\vskip .25cm
%``What Makes a Landmark Supreme Court Case? A Dynamic Analysis of How Non-Ideological Coalitions Predict Landmark Decisions" 
%\vskip .25cm
%\vskip .25cm
%``Beyond the Closet: An Exploratory Study of Sexual Minority Representation in the American Context" (with Matthew Yarbrough) 



%Languages skills: English (native), French (professional proficiency) 

\subsection*{\textbf{TEACHING EXPERIENCE in Methods, American Politics, and International Relations/Affairs}}

\textbf{University of Missouri (Undergraduate):} 
\vskip .25cm
Introduction to Political Research -- Writing Intensive. Fall 2022. \\ 

\textbf{University of Missouri (Graduate):} 
\vskip .25cm
Research Methods and Inquiry in Public Affairs (Master's). Fall 2022. \\


\textbf{University of Colorado Boulder (Undergraduate):} 
\vskip .25cm
Applied Political Science Research (Instructor of Record). Spring 2022.  \\
Introduction to American Politics (Teaching Assistant). Fall 2017-Spring 2018, Fall 2018-Spring 2019. \\
Quantitative Research Methods (Teaching Assistant). Fall 2019. Fall 2021. \\ 
Methods Lab Coordinator. Fall 2020-Spring 2021. \\ 
Introduction to International Affairs (Teaching Assistant). Fall 2016. \\ 
International Political Economy (Teaching Assistant). Spring 2017. \\

\textbf{Other:} 
\vskip .25cm
Panel and Longitudinal Analysis, ICSPR Methods Summer School (Teaching Assistant). July-August 2021.  \\
Advanced Time Series Cross Section Analysis, IPSA Methods Summer School at University of S\~{a}o Paulo (Teaching Assistant). January 2019. January 2020. \\


%\vskip .25cm

%\textbf{Additional teaching interests}: American political behavior, time series and pooled time series, introduction to comparative politics, immigration politics, race, inequality, and political engagement, women and politics, politics of Western Europe

\subsection*{\textbf{FUNDING AND RESEARCH AWARDS}}
Travel Award from MPSA's Women's Caucus for Political Science. 2022.
\vskip .25cm
Graduate Students in Political Science Paper Prize, Third Prize in 2021. First Prize in 2018.
\vskip .25cm
Graduate School Summer Fellowship, University of Colorado Boulder Graduate School. 2020.
\vskip .25cm
Large Graduate Research Grant Award, University of Colorado Boulder Political Science Department. 2019, 2020.
\vskip .25cm
International Travel Grant Award, University of Colorado Boulder Graduate School. 2019.
\vskip .25cm
%Carrie Chapman Catt Prize for Research on Women and Politics, Declined. 2019. 
%\vskip .25cm
Society for Political Methodology's National Science Foundation Award. 2018.
\vskip .25cm
Teamwork Grant for research project, University of Colorado Boulder Political Science Department, ``What goes up must come down: Modeling non-linear dynamics" with Andrew Philips. 2018.
\vskip .25cm
Beverly Sears Graduate Student Research Grant. 2018.
\vskip .25cm
Best Comparative Politics Poster, International Political Science Association -- University of S\~{a}o Paulo Summer School in Concepts, Methods and Techniques in Political Science and International Relations, First Prize. 2018
\vskip .25cm
Center to Advance Research and Teaching in the Social Sciences (CARTSS) Grant. 2017.
\vskip .25cm
Teamwork Grant for research project, University of Colorado Boulder Political Science Department, ``Immigration Politics in Context" with Jennifer Fitzgerald. 2017.
\vskip .25cm
CU Boulder Political Science Graduate Research Grant. 2017, 2018.
\vskip .25cm
%Domestic Travel Grant Award, University of Colorado Boulder Graduate School. 2017, 2018, 2021.
%\vskip .25cm
Best First Year Poster Presentation, University of Colorado Boulder Political Science Department, 
Second Prize. 2016.	
\vskip .25cm
Fulbright Research Fellowship to France, Finalist. 2013.


%\subsection*{\textbf{RESEARCH EXPERIENCE}}
%Research Assistant for Andrew Philips, CU Boulder. 2018-present.
%\vskip .25cm
%Research Assistant for Jennifer Fitzgerald, CU Boulder. 2016-present.
%\vskip .25cm
%Research Assistant for Carew Boulding, CU Boulder. Summer 2017, 2018, 2020.
%\vskip .25cm
%Research Associate for Vanessa Bouche, co-Principal Investigator, ``Effective Counter-Trafficking Practices in the United States: Legislative, Legal, and Public Opinion Strategies that Work." National Institute of Justice. 2013.
%\vskip .25cm
%Research Fellow, Democracy, Interdependence and World Politics Summer Research Program, National Science Foundation. 2012.

\subsection*{\textbf{SOFTWARE PROFICIENCY}}
Stata, \texttt{R}, \LaTeX \par

\subsection*{\textbf{INVITED TALKS}}
``How to Cautiously Uncover the `Black Box' of Machine Learning Models." (with Soren Jordan and Andrew Q. Philips), International Methods Colloquium, Virtual. June 2020.  
\vskip .25cm
``Roundtable on Measuring Identity and Evaluation its Effects." (with Ed Schatz), IPSA-USP Summer School in Concepts, Methods and Techniques in Political Science, Public Policy and International Relations, S\~{a}o Paulo. January 2020. 
\vskip .25cm

\subsection*{\textbf{RECENT CONFERENCE PRESENTATIONS}}
``A Bitter ALE: Making the Most of Accumulated Local Effects (ALE) Plots." (with Soren Jordan and Andrew Q. Philips. Midwest Political Science Association, Chicago. April 2022. 
\vskip .25cm
``What Goes up Must Come Down: Modeling Threshold Dynamics." (with Andrew Q. Philips), Visions in Methodology, Claremont. November 2021. 
\vskip .25cm
``Refuge and Representation: An Examination of Party Support among Refugees in Germany," Midwest Political Science Association, Virtual. April 2021.  
\vskip .25cm
``Critical Mass Theory: In Search of Vital Signs." (with Kendall D. Funk and Andrew Q. Philips), Conference on Quantitative Methods and Gender \& Politics, College Station. March 2019. 
\vskip .25cm
``What Goes up Must Come Down: Modeling Non-linear Dynamics." (with Andrew Q. Philips), Annual meeting of the Society for Political Methodology, Provo. July 2018. 
\vskip .25cm
``Beyond the Closet: An Exploratory Study of Sexual Minority Political Ambition in the American 
Context" (with Matthew Yarbrough), Annual meeting of Western Political Science Association, San Francisco. March 2018.
\vskip .25cm
``The Dynamics of Issue Salience: Immigration and Political Behavior" (with Jennifer Fitzgerald), Annual meeting of American Political Science Association, San Francisco. August 2017.
\vskip .25cm
``Public Discourse and Immigrant Assimilation: Incompatibility and the Othering of Immigrant Groups," Annual meeting of International Studies Association, San Francisco. April 2013.



\subsection*{\textbf{PROFESSIONAL MEMBERSHIP}}
 %Reviewer, {\it Journal of This, Journal of That, Journal of Other Things}.
 %\vskip .25cm
\textbf{Member}:  Midwest Political Science Association, American Political Science Association, The Society for Political Methodology, International Studies Association, Western Political Science Association 

%\subsection*{\textbf{DEPARTMENTAL SERVICE}}

%\subsubsection*{Committees}
%\textbf{2022-2023}: Lectures, Undergraduate \par


%\subsubsection*{Graduate Student Service}
%\textbf{Member}: Racial Justice Task Force, Dept. of Political Science, University of Colorado Boulder. 2020-2021 \par
%\textbf{Graduate Teaching Program Lead}, University of Colorado Boulder. 2019-2020. \par
%\textbf{President}: Graduate Students in Political Science, University of Colorado Boulder. 2019-2020. \par
%\textbf{Coordinator}: Mentors of Political Science, University of Colorado Boulder. 2018-2019. \par
%\textbf{Vice President}: Graduate Students in Political Science, University of Colorado Boulder. 2017-2018. \par
% \textbf{Graduate Student Mentor}: Mentors of Political Science, University of Colorado Boulder. 2017-2018. \par



%\subsection*{\textbf{REFERENCES}}
%\begin{minipage}[t]{.5\textwidth}
%{\centering
% \vskip .25cm
%\textbf{X}\\
%Dr. Jennifer Fitzgerald\\
%Department of Political Science\\
%University of Colorado Boulder\\
%333 UCB, Boulder, CO 80309 \\
%\href{mailto:Jennifer.Fitzgerald@colorado.edu}{jennifer.fitzgerald@colorado.edu}\\

%\vspace{10mm}
%\textbf{Y}\\
%Dr. Carew Boulding\\
%Department of Political Science\\
%University of Colorado Boulder\\
%333 UCB, Boulder, CO 80309 \\
%\href{mailto:carew.boulding@colorado.edu}{carew.boulding@colorado.edu}\\



%}
%\end{minipage}
%\begin{minipage}[t]{.5\textwidth}{\centering
%\vskip .25cm
%\textbf{Z}\\
%Dr. Andrew Q. Philips\\
%Department of Political Science\\
%University of Colorado Boulder\\
%333 UCB, Boulder, CO 80309 \\
%\href{mailto:Andrew.Philips@colorado.edu}{andrew.philips@colorado.edu}\\


%\vspace{10mm}
%\textbf{M}\\
%Dr. Anand Sohkey\\
%Department of Political Science\\
%University of Colorado Boulder\\
%\href{mailto:anand.sokhey@colorado.edu }{anand.sokhey@colorado.edu }\\



%}

%\end{minipage}

\vfill{}

\begin{center}
{\scriptsize  Last updated: \today }
% ---- FILL IN THE FULL URL TO YOUR CV HERE
% \href{www.politcal.com/CV}{www.politcal.com/CV}}
\end{center}

\end{document}